A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-17 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{We have discussed several state-of-the-art anchor free Siamese trackers at the related work. For your convenience of cross review, the new text is given as follows.}

\uline{
% Ocean
Ocean \cite{zhang2020ocean} directly predicts the position and scale of target objects in an anchor-free fashion. Since each pixel in groundtruth boxes is well trained, the tracker is capable of rectifying inexact predictions of target objects during inference.
% FCOT
FCOT \cite{cui2020fully} introduces an online regression model generator (RMG) based on the carefully designed anchor-free box regression branch, which enables the tracker to be more effective in handling target deformation during tracking procedure.
%  SiamCAR
SiamCAR \cite{9157720} is both proposal and anchor free, and decomposes tracking into two subproblems: one classification problem and one regression task. SiamCAR takes one unique response map to predict object location and bounding box directly.
}

\textbf{Besides, we have evaluated the transferability to the anchor free tracker OCEAN in Setcion IV.E of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\begin{table}[t]
  \renewcommand\thetable{XV}
  \centering
  \caption{Transferability to different tracking architectures on OTB2015. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more state-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO    & Precision \\ \midrule
  SiamRPN++                 & 0.676   & 0.879             & 0.418 & 0.556     \\
  SiamRPN                   & 0.666   & 0.876             & 0.483 & 0.643     \\
  Ocean                     & 0.672   & 0.902             & 0.237 & 0.282     \\ \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}
\uline{\textit{Transferability to Different Tracking Architectures} We evaluate the transferability of our attacks when applying the perturbations to three more tate-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}. SiamRPN and SiamRPN++ are ahchor-based trackers, and Ocean is an anchor-free tracker. The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the \textit{real trajectory} drops from 0.666 to 0.483 and the performance of SiamRPN++ is decreased from 0.676 to 0.418. In the case of Ocean, the AO with respect to the \textit{real trajectory} drops from 0.902 to 0.282. The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.
}

### 2021-09-17 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
改caption

%%%%%%%% 不同跟踪器的可迁移性 %%%%%%%%
\begin{table}[t]
  \centering
  \caption{Transferability to different tracking architectures on OTB2015. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more state-of-the-art anchor-based trackers: AlexNet-based SiamRPN \cite{SiamRPN} and ResNet-based SiamRPN++ \cite{SiamRPN++}.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO & Precision                   \\
  \midrule
  SiamRPN++                 & 0.676   & 0.879                  & 0.418   & 0.556                       \\
  SiamRPN                   & 0.666   & 0.876                  & 0.483   & 0.643                       \\
  Ocean                     & 0.672   & 0.902             & 0.237 & 0.282     \\ \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}
\uline{\textit{Transferability to Different Tracking Architectures} We evaluate the transferability of our attacks when applying the perturbations to three more tate-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}. SiamRPN and SiamRPN++ are ahchor-based trackers, and Ocean is an anchor-free tracker.
%SiamRPN uses an RPN network to perform location regression and target classification on the response maps. SiamRPN++ performs layer-wise and depth-wise aggregation to improve accuracy based on the effective training using the ResNet backbone. 
The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the \textit{real trajectory} drops from 0.666 to 0.483 and the performance of SiamRPN++ is decreased from 0.676 to 0.418.
In the case of Ocean, the AO with respect to the \textit{real trajectory} drops from 0.902 to 0.282.
%We further analyze the performance of our attack method with respect to 11 attributes in OTB-2015 \cite{OTB}. As suggested in OTB \cite{OTB}, the attributes consist of out-of-view (OV), occlusion (OCC), illumination variation (IV), out-of-plane rotation (OPR), scale variation (SV),deformation (DEF), low resolution (LR), fast motion (FM), background clutters (BC), motion blur (MB), and in-plane rotation (IPR). Figure \ref{fig:attr} illustrates the untargeted attack results of the aforementioned trackers under the 11 attributes. 
The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.
}

>>>>

%%%%%%%% 不同跟踪器的可迁移性 %%%%%%%%
\begin{table}[t]
  \centering
  \caption{Transferability to different tracking architectures on OTB2015. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more state-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO & Precision                   \\
  \midrule
  SiamRPN++                 & 0.676   & 0.879                  & 0.418   & 0.556                       \\
  SiamRPN                   & 0.666   & 0.876                  & 0.483   & 0.643                       \\
  Ocean                     & 0.672   & 0.902             & 0.237 & 0.282     \\ \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}
\uline{\textit{Transferability to Different Tracking Architectures} We evaluate the transferability of our attacks when applying the perturbations to three more tate-of-the-art trackers: SiamRPN \cite{SiamRPN}, SiamRPN++ \cite{SiamRPN++} and Ocean \cite{zhang2020ocean}. SiamRPN and SiamRPN++ are ahchor-based trackers, and Ocean is an anchor-free tracker.
%SiamRPN uses an RPN network to perform location regression and target classification on the response maps. SiamRPN++ performs layer-wise and depth-wise aggregation to improve accuracy based on the effective training using the ResNet backbone. 
The experimental results are shown in Table \ref{tab:arch}. In the case of SiamRPN, the AO with respect to the \textit{real trajectory} drops from 0.666 to 0.483 and the performance of SiamRPN++ is decreased from 0.676 to 0.418.
In the case of Ocean, the AO with respect to the \textit{real trajectory} drops from 0.902 to 0.282.
%We further analyze the performance of our attack method with respect to 11 attributes in OTB-2015 \cite{OTB}. As suggested in OTB \cite{OTB}, the attributes consist of out-of-view (OV), occlusion (OCC), illumination variation (IV), out-of-plane rotation (OPR), scale variation (SV),deformation (DEF), low resolution (LR), fast motion (FM), background clutters (BC), motion blur (MB), and in-plane rotation (IPR). Figure \ref{fig:attr} illustrates the untargeted attack results of the aforementioned trackers under the 11 attributes. 
The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.
}
